\mytitle

### 2023-05-11 chapters/intro.tex
intro todos

% In order to ameliorate the burden \todo{continue} Various areas of work have
% aimed to limit the burdens ,

@@

\section{Synthesis for In-Kernel JIT Compilers}
Modern operating systems have become increasingly extensible and customizable.
One way these systems enable customization is by
allowing users to submit custom code for kernel execution
written in an \textit{in-kernel DSL}.
Initially designed for network packet filtering, 
in-kernel DSLs like eBPF \todo{cite} enable kernel extentions
such as performance monitoring, load balancing, and intrusion detection.\todo{cite https://ebpf.io/case-studies/}
For performance reasons, operating systems use just-in-time (JIT) compilers
to execute in-kernel DSL programs.
However,
% as mentioned previously, % TODO?
these JIT compilers can be the source of major kernel bugs.\todo{cite}
Moreover, writing JIT compilers can pose a substantial effort to developers,
requiring on the order of thousands of lines of code.\todo{cite}

In \cref{c:jitsynth}, I present \jitsynth, a program synthesis tool that
automatically generates JIT compilers for in-kernel DSLs
given a specification of the source and target language.
Existing work has demonstrated how the correctness of JIT compilers
can be proven manually\todo{cite},
but the effort of such proofs is highly non-trivial.
By synthesizing JIT compilers, developers both avoid the burden of implementing
such systems \textit{and} can guarantee correctness
without requiring intensive proofs.

@@

\cref{c:depsynth} presents \depsynth, a tool for automatically generating crash consistency
code for storage systems.
\depsynth takes advantage of the observation
(identified in previous work \todo{cite Featherstitch})
that crash consistency mechanisms fundamentally enforce \textit{write-before relationships}.
To automate crash consistency,
\depsynth takes as input the implementation of a (non-crash consistent) storage system together
with a set of example programs over the system called \textit{litmus tests}.
The output is a set of \textit{dependency rules} which specify, at runtime,
the required write-before relationships to enforce.

% TODO revise this paragraph
We take advantage of several novel abstractions in order enable
automatic crash consistency with \depsynth.
First, we assume a new \textit{angelic crash consistency} model
that delegates enforcement of write-before relationships to a
\textit{dependency-aware buffer cache},
which sits between the storage system software and disk hardware layers.
Second, we introduce a language for dependency rules
that allows for both \textit{expressive} and \textit{generalizable} rules.
Finally, we describe a new search for dependency rules
directed by input litmus tests.
These insights enable \depsynth to synthesize dependency rules for an existing
production key-value store at Amazon\todo{cite shardstore} in 49\todo{macro this} minutes.

>>>>

@@

\section{Synthesis for In-Kernel JIT Compilers}
Modern operating systems have become increasingly extensible and customizable.
One way these systems enable customization is by
allowing users to submit custom code for kernel execution
written in an \textit{in-kernel DSL}.
Initially designed for network packet filtering, 
in-kernel DSLs like eBPF \cite{fleming:ebpf} enable kernel extentions
such as performance monitoring, load balancing, and intrusion detection
\cite{engler:vcode,fleming:ebpf,mccanne:bpf}.
For performance reasons, operating systems use just-in-time (JIT) compilers
to execute in-kernel DSL programs.
However,
% as mentioned previously, % TODO?
these JIT compilers can be the source of major kernel bugs
\cite{gpz:1454,paul:cve-2020-8835,blazakis:jit-spraying,kocher:spectre}.
Moreover, writing JIT compilers can pose a substantial effort to developers,
requiring on the order of thousands of lines of code.

In \cref{c:jitsynth}, I present \jitsynth, a program synthesis tool that
automatically generates JIT compilers for in-kernel DSLs
given a specification of the source and target language.
Existing work has demonstrated how the correctness of JIT compilers
can be proven manually\cite{wang:jitk,sobel:ejitk},
but the effort of such proofs is highly non-trivial.
By synthesizing JIT compilers, developers both avoid the burden of implementing
such systems \textit{and} can guarantee correctness
without requiring intensive proofs.

@@

\cref{c:depsynth} presents \depsynth, a tool for automatically generating crash consistency
code for storage systems.
\depsynth takes advantage of the observation
(identified in \cite{frost:featherstitch})
that crash consistency mechanisms fundamentally enforce \textit{write-before relationships}.
To automate crash consistency,
\depsynth takes as input the implementation of a (non-crash consistent) storage system together
with a set of example programs over the system called \textit{litmus tests}.
The output is a set of \textit{dependency rules} which specify, at runtime,
the required write-before relationships to enforce.

% TODO revise this paragraph
We take advantage of several novel abstractions in order enable
automatic crash consistency with \depsynth.
First, we assume a new \textit{angelic crash consistency} model
that delegates enforcement of write-before relationships to a
\textit{dependency-aware buffer cache},
which sits between the storage system software and disk hardware layers.
Second, we introduce a language for dependency rules
that allows for both \textit{expressive} and \textit{generalizable} rules.
Finally, we describe a new search for dependency rules
directed by input litmus tests.
These insights enable \depsynth to synthesize dependency rules for an existing
production key-value store at Amazon \cite{bornholt:s3} in \shardstoresynthesistime minutes.
